Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-24 BN_discretizer_paper.tex
appendix text

The Bayesian network structure in Figure \ref{fig:auto_graph_3} and the discretization results in Table \ref{table:auto_disc_table_3} demonstrate that the MDL method does not always return smaller number of discretization intervals than the Bayesian approach and also the MDL method can return a comparable result in terms of likelihood. The Bayesian network in Figure \ref{fig:auto_graph_3} is obtained by running Algorithm \ref{alg:structure_learn} fifty times with $u_{\text{parent}} = 2$. Therefore, this network can be considered more well-structured than the one in Figure \ref{fig:auto_graph_1}, since the effect of discretization policies has already been considered in the learning process.
Many edges appears in both discretization results, as the bold numbers in Table \ref{table:auto_disc_table_3}.
\begin{figure}[ht]
  \centering
  \scalebox{0.8}{
   \input{graph_autocar_3}}
   \caption{A Bayesian network structure for Auto MPG dataset that leads to a comparable discretization result of the MDL method with the Bayesian method}
  \label{fig:auto_graph_3}
\end{figure}

\begin{table}[h]
  \centering
  \caption{
    Results from discretization of the Auto MPG dataset with fixed structure from Figure~\ref{fig:auto_graph_3}.
    The first five rows list the discretization edges for each continuous variable.
    The last row lists the mean cross-validated log-likelihood.
    Two methods have same discretization result on variable $A$.
    Log-likelihood shows that the MDL method is just slightly worse than the Bayesian method.
  }
\input{table_autoMPG_3.tex}
  \label{table:auto_disc_table_3}
\end{table}
\end{document}
% end of file template.tex

>>>>

The Bayesian network structure in Figure~\ref{fig:auto_graph_3} and the discretization results in Table~\ref{table:auto_disc_table_3} demonstrate that the MDL method does not always produce fewer discretization intervals than the Bayesian approach and that the MDL method can produce discretization policies with comparable likelihood.
The Bayesian network in Figure~\ref{fig:auto_graph_3} was obtained by running Algorithm~\ref{alg:structure_learn} fifty times on the Auto MPG dataset with a maximum of two parents per variable.
The network is more well-structured than the one in Figure~\ref{fig:auto_graph_1}, because the discretization policies were simultaneously learned with the network structure.
Many edges appears in both discretization results, and are bolded in Table~\ref{table:auto_disc_table_3}.

\begin{figure}[ht]
  \centering
  \scalebox{0.8}{\input{graph_autocar_3}}
  \caption{A Bayesian network structure for the Auto MPG dataset that leads to comparable discretization policies from the MDL and Bayesian methods.}
  \label{fig:auto_graph_3}
\end{figure}

\begin{table}[h]
  \centering
  \caption{
    The discretization policies for the Auto MPG dataset with the fixed structure shown in Figure~\ref{fig:auto_graph_3}.
    The first five rows list the discretization edges for each continuous variable.
    The last row shows the mean cross-validated log-likelihood under each policy.
    The methods have same discretization result on variable $A$, and the log-likelihood for the MDL method only just slightly worse than that of the Bayesian method.
  }
\input{table_autoMPG_3.tex}
  \label{table:auto_disc_table_3}
\end{table}
\end{document}
% end of file template.tex
